Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2020-10-27 paper/main.tex
fix sec 4

\subsubsection{Other}.  For simplicity, we use Kendall's $\tau$
distance~(Eq.~\ref{eq:kendall_decomp}) in all
experiments\MANUEL{\citet{ZaeStoBar2014:ppsn} claims this is called Swap
  distance, could you double-check?\ekhine{}{es la kendall among the inverses en realidad}}. Nevertheless,
\citet{ZaeStoFriFisNauBar2014} points out that CEGO performs best on the QAP
when using Hamming distance.  We plan to extend UMM to other distance measures
and to the dynamic selection of distance measures~\citep{ZaeStoBar2014:ppsn}.
In all experiments, we consider a maximum budget of $\FEmax=400$ evaluations of
the actual objective function. In a white-box context, state-of-the-art
algorithms for the problems considered here typically evaluate
thousands of solutions, thus, the budget considered
here for the black-box context is extremely limited.

>>>>

\subsubsection{Other settings}.  For simplicity, we use Kendall's $\tau$
distance~(Eq.~\ref{eq:kendall_decomp}) in all
experiments. Nevertheless,
\citet{ZaeStoFriFisNauBar2014} points out that CEGO performs best on the QAP
when using Hamming distance.  We plan to extend UMM to other distance measures.
In all experiments, we consider a maximum budget of $\FEmax=400$ evaluations of
the actual objective function. In a white-box context, state-of-the-art
algorithms for the problems considered here typically evaluate
thousands of solutions, thus, the budget considered
here for the black-box context is extremely limited.
